### 2021-06-18 paper/appendix_results.tex
Polish model summary.
Add explanation on shapley values.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_demand}
  \caption{Share of Individuals that Demand a Rapid Test for a Particular Reason that are Actually Infected}
  \label{fig:share_of_rapid_tests_by_reason_by_infected}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that this is not the same as individuals getting a positive rapid test. The
  sensitivity is quite low before individuals become infectious. Therefore, if
  individuals are still in the latent period of their infection they are likely to get a
  false positive rapid test.}
\end{figure}

@@

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_demand}
  \caption{Share of individuals who Demand a Rapid Test for a Particular Reason that are Actually Infected}
  \label{fig:share_of_rapid_tests_by_reason_by_infected}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that this is not the same as individuals getting a positive rapid test. The
  sensitivity is quite low before individuals become infectious. Therefore, if
  individuals are still in the latent period of their infection they are likely to get a
  false positive rapid test.}
\end{figure}

@@

\subsection{Shapley Value} % (fold)
\label{sub:shapley_value}

We decompose the effects of different NPIs and seasonality on the infection rates with
Shapley values. Shapley values \citep{Shapley2016} are a concept in game theory to
divide payoffs between a coalition of players. It allows to assign a single value to the
contribution of an NPI or seasonality which takes into account substitutional and
complementary effects with other factors.

More formally, define a coalitional game with $N$ players and a super-additive function
$\nu$ which maps subsets of $N$ to the real numbers. The function $\nu$ is also called
the characteristic function and assigns a value to a coalition. Then, the Shapley value
$\phi$ for player $i$ is

\begin{align*}
    \phi_i(\nu) = \frac{1}{|N| !} \sum_{S \subseteq N \setminus \{i\}} |S| ! (|N| - |S| - 1)! (\nu(S \cup \{i\}) - \nu(S))
\end{align*}

The last term $(\nu(S \cup \{i\}) - \nu(S))$ is the marginal contribution of player $i$
minus the coalition without player $i$. Then, compute the sum of marginal contributions
over all subsets $S$ of $N$ which do not include player $i$. Each marginal contribution
has to be multiplied by all combinations of other players in $S$ which precede $i$ and
all possible combinations of remaining players which follow player $i$ in the coalition.
To arrive at the Shapley value for player $i$, divide the sum by the total number of
combinations.

The Shapley value has some properties.

\begin{description}
  \item[Efficiency] The sum of Shapley values is equal to the value of a coalition
  formed by all players.
  \item[Symmetry] The Shapley does not depend on the label of a player but only on its
  position in the characteristic function.
  \item[Linearity] The Shapley value depends linearly on the values from the
  characteristic function $\nu$.
  \item[Dummy Axiom] The Shapley value of a player who contributes nothing to any
  coalition is 0.
\end{description}

To produce Figure~\ref{fig:2021_scenarios_decomposition} and
Figure~\ref{fig:2021_scenarios_decomposition_tests}, we calculate the Shapley values of
each factor in the comparison on the cumulative number of saved infections between the
main scenario and the scenario without any of the factors for every day. Then, we divide
up the saved infections on a particular day according to the Shapley values for the same
day which yields the daily saved infections for each factor.

% subsection shapley_value (end)

### 2021-06-18 paper/report.tex
Add explanation on shapley values.

    \floatfoot{\noindent \textit{Note:} The blue line in
        Figure~\ref{fig:2021_scenarios_recorded} is the same as in
        Figure~\ref{fig:aggregated_fit} and refers to our baseline scenario, so does the
        blue line in Figure~\ref{fig:2021_scenarios_newly_infected}. The red lines refer
        to a situation where NPIs evolve as in the baseline scenario and the B.1.1.7
        variant is introduced in the same way; vaccinations, rapid tests, and
        seasonality remain at their January levels. The other scenarios turn these three
        factors on one-by-one. The decompositions in
        Figures~\ref{fig:2021_scenarios_decomposition} and
        \ref{fig:2021_scenarios_decomposition_tests} are based on Shapley values where
        the individual contribution of a channel is its average contribution over
        different sizes of coalitions (combinations with other channels). The individual
        contribution to a coalition is the difference between the effect size of the
        coalition with the particular channel and without.}
\end{figure}

>>>>

    \floatfoot{\noindent \textit{Note:} The blue line in
        Figure~\ref{fig:2021_scenarios_recorded} is the same as in
        Figure~\ref{fig:aggregated_fit} and refers to our baseline scenario, so does the
        blue line in Figure~\ref{fig:2021_scenarios_newly_infected}. The red lines refer
        to a situation where NPIs evolve as in the baseline scenario and the B.1.1.7
        variant is introduced in the same way; vaccinations, rapid tests, and
        seasonality remain at their January levels. The other scenarios turn these three
        factors on one-by-one. The decompositions in
        Figures~\ref{fig:2021_scenarios_decomposition} and
        \ref{fig:2021_scenarios_decomposition_tests} are based on Shapley values which
        are explained more thoroughly in Appendix~\ref{sub:shapley_value}}
\end{figure}
